%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\usepackage{amsfonts,amsmath,amssymb,amsbsy,amstext,amsthm,mathtools}

\newcommand{\C}{\mathbb{C}}
\newcommand{\PP}{\mathbb{P}}


\name{Nesime Tatbul} % used as signature, if no signature is specified

\signature{Juliette Bruce}

\date{April 5, 2024} % if no date specified, today's date is used 

%\subject{Application for Lecturer Posititon} % optional subject line

\begin{document}

\begin{letter}{Juliette Bruce\\ 
               Brown University\\ 
               Providence, RI 02912}

\opening{Dear Committee Members,}

I am writing to apply for a lecturer position in the Department of Mathematics at San Francisco State University. Currently, I am a postdoctoral researcher in the Mathematics Department at Brown University, a position I have held since August 2022. I received my Ph.D. in Mathematics from the University of Wisconsin - Madison in 2020 under the guidance of my advisor Professor Daniel Erman. From 2020-2022 I was an NSF Postdoctoral Fellow in the Mathematics Department at the University of California, Berkeley.



My research interests lie in the intersection of algebraic geometry and commutative algebra. Further, I am passionate about promoting inclusivity, diversity, and justice in the mathematics community. This passion extends throughout my teaching where I am dedicated to creating an interactive, engaging, and supportive classroom environment that helps students thrive. I would be interested, and feel qualified, in teaching any of the lower-division courses (numbered below 300) along with 325. While I feel slightly less qualified I also believe that I could successfully teach either  324 or 565 if needed. Having read through the course bulletin the courses that are of particular interest to me are: 199, 225, 226, 227, and 325, but I would be very happy teaching any of the other above mentioned courses as well. 

Despite my recent positions having excluded formal teaching duties, I have found novel ways to explore my passion for teaching and supporting students. For example, I have organized multiple online educational opportunities for undergraduate math students, including two summer research programs and a virtual directed reading program in algebra and geometry. Further, I have worked to support LGBTQ+ and other minority students by organizing events that help such students find mentors and support.  

With my application I have included my curriculum vitae, my publication list, a brief teaching statement with supporting materials, and three letters of recommendation. A few highlights in my file are:
\begin{itemize}

\item Capstone Teaching Award (2019) - Awarded by the Department of Mathematics at the University of Wisconsin to 1 student recognizing a record of exceptional teaching and service.
\item Teaching Assistant Award for Exceptional Service  (2018) - Awarded by the University of Wisconsin to up to 3 teaching assistants campus-wide recognizing their exceptional service.

\end{itemize}

Please contact me with any questions, and thank you in advance for your consideration.
\vspace{.1 in}
\\
Sincerely,
\\
Juliette Bruce

% \encl{brownletter.cls}

% \ps{Please see the enclosed file.}

% \cc{J. Kirschenbaum}

\end{letter}

\end{document}