% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008-2014 Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
%
% Depending on your TeX distribution, you may need to download the revnum and longtable packages for this template to work!
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\usepackage{amstext,amsfonts,amssymb,amscd,amsbsy,amsmath}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage{array}
\usepackage[svgnames]{xcolor}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{longtable}
\usepackage{revnum}
\usepackage{textcomp}

\usepackage[colorlinks=true,urlcolor=blue,hyperfootnotes=false]{hyperref}
\usepackage{tocloft}
\usepackage{array}

\usepackage[symbol]{footmisc}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
\setlength\LTleft{0.2in} % needed to make longtable full-width
\setlength\LTright{0.2in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\fboxsep}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

% the next four commands allow for the \ressubheading environment to be 1, 2, 3, or 4 subrows, depending on which command you use. This is admittedly hack-ish, and should probably be replaced by a single more flexible command (with optional arguments) in the future
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadingTalk}[2]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		#1 & #2 \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingTalkBold}[2]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingb}[6]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadingc}[8]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
		\textit{#7} & \textit{#8} \\
\end{tabular*}\vspace{-6pt}}
\newcommand\foo[9]{%
    \def\tempb{#2}%
    \def\tempc{#3}%
    \def\tempd{#4}%
    \def\tempe{#5}%
    \def\tempf{#6}%
    \def\tempg{#7}%
    \def\temph{#8}%
    \def\tempi{#9}%
    \foocontinued
}
\newcommand\foocontinued[7]{%
    % Do whatever you want with your 9+7 arguments here.
}

\newcommand{\ressubheadingd}[1]{
	\def\argten{#1}%
	\ressubheadingdb
}
\newcommand{\ressubheadingdb}[9]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{\argten} & #1 \\
		\textit{#2} & \textit{#3} \\
		\textit{#4} & \textit{#5} \\
		\textit{#6} & \textit{#7} \\
		\textit{#8} & \textit{#9} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\usepackage[lf]{Baskervaldx}

\begin{document}

{\large \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\LARGE Juliette Newton}\smallskip & \textbf{\today}\smallskip \\
Department of Mathematics & \\
Brown University & juliette\_bruce1@brown.edu \\
990 Ducan St. 207G & \hyperref{https://www.juliettebruce.xyz}{}{}{https://www.juliettebruce.xyz} \\
San Francisco, CA 94131 & \\
\end{tabular*}}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item \ressubheading{Math 110: Business Calculus }{San Francisco State University}{Instructor}{Spring 2023}

\item \ressubheading{Math 198: Pre-Calculus II}{San Francisco State University}{Instructor}{Spring 2023}
	
\item \ressubheading{Math 197: Pre-Calculus I}{San Francisco State University}{Instructor}{Fall 2023}
	\begin{itemize}
		\resitem{Sections ranged from 25-35 students on average, with typically teaching two sections at a time.}
	\end{itemize}
	
\item \ressubheading{Math 107/110: Business Calculus }{San Francisco State University}{Instructor}{Fall 2023}
	\begin{itemize}
		\resitem{Selected to have courses be part of the Metro College Success Program based on history of supporting underserved students. }
		\resitem{Sections ranged from 25-35 students on average, with typically teaching two sections at a time.}
	\end{itemize}

\item 
	\ressubheading{Math 221: Calculus and Analytic Geometry I}{University of Wisconsin}{Teaching Assistant}{Fall 2014/2018/2019}
	\begin{itemize}
		\resitem{Selected as a TA coordinator in 2018 and 2019, and was responsible for overseeing all other TA's and mentoring first year TA's.}
		\resitem{Sections ranged from 25-35 students on average, with typically teaching two sections at a time.}
		\resitem{Average score 4.9/5.0}
	\end{itemize}
	
\item 
	\ressubheading{Math 228: Wisconsin Emerging Scholars}{University of Wisconsin}{Instructor}{Fall 2018}
	\begin{itemize}
		\resitem{Course providing students from underrepresented groups additional support.}
		\resitem{Course had approximately 10-15 students.}
		\resitem{Average score: 5.0/5.0, 100\% amongst all TA's}
	\end{itemize}

\item 
	\ressubheading{Math 132: PProblem Solving in Algebra, Statistics, \& Probability}{University of Wisconsin}{Instructor}{Spring 2015}
	\begin{itemize}
		\resitem{Course had approximately 15-25 students.}
		\resitem{Responsible for all aspects of the course.}
	\end{itemize}

\item 
	\ressubheading{Inquiry Based Learning Courses}{University of Michigan}{Course Assistant}{2012-2014}
		\begin{itemize}
		\resitem{Assisted with advanced undergraduate courses on topology, analysis, and probability. }
		\resitem{Courses had approximately 25-35 students.}
		\resitem{Facilitated inquiry based learning in the classroom, and responsible for office hours, grading, and review sessions.}
		\end{itemize}

\item 
	\ressubheading{Math 310: Explorations in Randomness}{University of Michigan}{Course Assistant}{Winter 2014}
	\begin{itemize}
		\resitem{Assisted facilitating inquiry based learning in the classroom.}
		\resitem{Responsible for office hours, grading, and review sessions.}
	\end{itemize}

\item 
	\ressubheading{Math 490: Introduction to Topology}{University of Michigan}{Course Assistant}{Fall 2013}
	\begin{itemize}
		\resitem{Assisted facilitating inquiry based learning in the classroom.}
		\resitem{Responsible for office hours, grading, and review sessions.}
	\end{itemize}
%
%\item 
%	\ressubheading{Graph Theory}{Michigan Math and Science Scholars}{Course Assistant}{Summer 2013}
%
\item 
	\ressubheading{Math 351: Principals of Analysis}{University of Michigan}{Course Assistant}{Winter 2013}

	
\item 
	\ressubheading{Math 105: Data, Functions, and Graphs}{University of Michigan}{Course Assistant}{Fall 2012}

%\item 
%	\ressubheading{Math Lab}{University of Michigan}{Tutor}{Fall 2011 -- Winter 2013}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Non-Standard Teaching Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{itemize}

%\item 
%	\ressubheading{Equity, Diversity, and Inclusion in Mathematics}{CAIMS}{Panelist}{June 2021}
%
%
%\item 
%	\ressubheading{Diversity and Inclusion Panel}{Womxn in Math at Berkeley}{Panelist}{April 2021}

\item 
	\ressubheading{Virtual Directed Readings in Geometry}{Held Virtually}{Organizer}{February 2021 -- April 2021}
	\begin{itemize}
		\resitem{Created a virtual, open access, directed reading program for undergraduate students.}
		\resitem{Approximately 30 students signed up for the 5-week reading group.}
	\end{itemize}

\item 
	\ressubheading{Algebraic Geometry in the Time of COVID}{Held Virtually}{Shepard}{June 2020 -- October 2020}
	\begin{itemize}
		\resitem{A virtual, open access introductory course in algebraic geometry.}
		\resitem{Approximately 1600 registered participants.}
	\end{itemize}
		
%\item 
%	\ressubheading{How to Stay Productive as a Researcher}{Lunch in the Time of COVID}{Panelist}{June 2020}
%
%\item 
%	\ressubheading{Mathematics Research Online: Hosting Virtual Events}{Held Virtually}{Panelist}{May 2020}
%
%\item 
%	\ressubheading{Supporting Transgender and Non-binary Students}{MAA Panel at the JMM}{Panelist}{January 2020}
%	
\item 
	\ressubheading{Undergrad Directed Reading Program}{University of Wisconsin}{Mentor}{January 2018 -- May 2019}
	\begin{itemize}
		\resitem{Lead two semester long reading projects on commutative algebra and algebraic geometry.}
		\resitem{Lead an undergraduate women on a two semester reading project, and provided guidance on applying for REU's and graduate school.}
	\end{itemize}
	
\item 
	\ressubheading{Graduate Peer Mentoring}{University of Wisconsin}{Mentor}{September 2018 -- December 2018}
	\begin{itemize}
		\resitem{Mentored 5 first year graduate students from minority genders, organizing monthly dinners where the mentees could discuss issues they were facing.}
	\end{itemize}
		
\item 
	\ressubheading{Girls Math Night Out}{University of Wisconsin}{Mentor}{September 2018 -- December 2018}
	\begin{itemize}
		\resitem{Lead 2 women from local high schools on a semesters long project about cryptography.}
	\end{itemize}

\item 
	\ressubheading{Madison Math Circle}{University of Wisconsin}{Lead Organizer}{January 2016 -- December 2018}
	\begin{itemize}
		\resitem{Lead the creation of a new outreach program, which directly visits high schools around the state of Wisconsin to better serve students from underrepresented groups.}
		\resitem{Expanded the total number of students reached per year from 25 to >250.}
	\end{itemize}

\item 
	\ressubheading{Madison Math Circle}{University of Wisconsin}{Student Volunteer}{January 2015 -- December 2018}
	

\end{itemize}
	
\end{document}