%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\usepackage{amsfonts,amsmath,amssymb,amsbsy,amstext,amsthm,mathtools}

\newcommand{\C}{\mathbb{C}}
\newcommand{\PP}{\mathbb{P}}


\name{Nesime Tatbul} % used as signature, if no signature is specified

\signature{Juliette Bruce}

\date{November 3, 2023} % if no date specified, today's date is used 

%\subject{Application for Lecturer Posititon} % optional subject line

\begin{document}

\begin{letter}{Juliette Bruce\\ 
               Brown University\\ 
               Providence, RI 02912}

\opening{Dear Committee Members,}

I am writing to apply for a position as a part-time lecturer in mathematics at Northeastern University. I am interested in this position because I am passionate about teaching and working with students, especially students from diverse backgrounds. Currently, I am a lecturer faculty member at San Francisco State University and a postdoctoral researcher in the Mathematics Department at Brown University. (Note that I live in San Francisco, CA, as I am working at Brown University remotely part-time.)  I received my Ph.D. in Mathematics from the University of Wisconsin-Madison in 2020 under the guidance of my advisor Professor Daniel Erman. From 2020-2022 I was an NSF Postdoctoral Fellow in the Mathematics Department at the University of California, Berkeley.

I am passionate about promoting inclusivity, diversity, and justice in the mathematics community. This passion extends throughout my teaching where I am dedicated to creating an interactive, engaging, and supportive classroom environment that helps students thrive. My goal as an educator is to be an active guide for students, providing them with environments where they feel supported and encouraged to let their own mathematical and quantitative curiosities guide how they engage and learn. By taking this approach, I hope to engage with students as the complete people that they are, asking them to bring all of their experiences, backgrounds, identities, and knowledge into the learning environment. I want students to experience mathematics in a humanistic way, seeing how mathematics and quantitative thinking are integral aspects of their lives. As one of my former students noted, ``Juliette obviously wants us to succeed not only in math but in life.''


With my application, I have included my curriculum vitae, a teaching statement, a diversity statement, and three reference letters. A few highlights in my file are:
\begin{itemize}

\item Capstone Teaching Award (2019) - Awarded by the Department of Mathematics at the University of Wisconsin to 1 student recognizing a record of exceptional teaching and service.
\item Teaching Assistant Award for Exceptional Service  (2018) - Awarded by the University of Wisconsin to up to 3 teaching assistants campus-wide recognizing their exceptional service.

\end{itemize}

Please contact me with any questions, and thank you in advance for your consideration.
\vspace{.1 in}
\\
Sincerely,
\\ \vspace{.1 in}

Juliette Bruce

% \encl{brownletter.cls}

% \ps{Please see the enclosed file.}

% \cc{J. Kirschenbaum}

\end{letter}

\end{document}