%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\usepackage{amsfonts,amsmath,amssymb,amsbsy,amstext,amsthm,mathtools}

\newcommand{\C}{\mathbb{C}}
\newcommand{\PP}{\mathbb{P}}


\name{Nesime Tatbul} % used as signature, if no signature is specified

\signature{Juliette Bruce}

\date{April 18, 2023} % if no date specified, today's date is used 

\subject{Application to Topos Institute Postdoc} % optional subject line

\begin{document}

\begin{letter}{Juliette Bruce,\\ 
               Brown University\\ 
               Box 1917\\ 
               Providence, RI 02912}

\opening{To the Hiring Committee,}

I am writing to apply for the postdoctoral research position at the Topos Institute. Currently, I am a Postdoctoral Research Association in the Mathematics Department at Brown University, a position I have held since August 2022. I received my Ph.D. in Mathematics from the University of Wisconsin - Madison in the Summer of 2020 under the guidance of my advisor Professor Daniel Erman. Previously I was an NSF Postdoctoral Research Fellow in the Mathematics Department at the University of California, Berkeley, and for the 2020-2021 academic year I was a Postdoctoral Fellow at the Mathematical Sciences Research Institute in Berkeley, CA.

My research interests lie in the intersection of algebraic geometry and commutative algebra. In particular, I am interested in using combinatorial, computational, and homological methods to study the geometry of zero loci of systems of polynomials (i.e. algebraic varieties). Further, I am passionate about promoting inclusivity, diversity, and justice in the mathematics community. However, recently I have become interested in using my mathematical 

With my application I have included my curriculum vitae. A few highlights in my file are:
\begin{itemize}
\item Invited to speak at the \textit{Western Algebraic Geometry Online} (April 2020), \textit{Foundations of Computing in Mathematics} (June 2020), and \textit{LGBTQ+Math} (July 2020).

\item Excellence in Mathematical Research Award (2020) - Awarded by the Department of Mathematics at the University of Wisconsin for substantial contributions to research as part of a thesis. 
%Elizabeth Hirschfelder Prize (2019) - Awarded by the Department of Mathematics at the University of Wisconsin to an outstanding female student who has demonstrated promise.

\item Co-organizer for seven conferences, two AMS special sessions, and numerous outreach events. Awarded approximately \$55,000 in grants to support these conferences.  

\item Capstone Teaching Award (2019) - Awarded by the Department of Mathematics at the University of Wisconsin to 1 student recognizing a record of exceptional teaching and service. Teaching Assistant Award for Exceptional Service  (2018) - Awarded by the University of Wisconsin to up to 3 teaching assistants campus-wide recognizing their exceptional service.
\end{itemize}

Please do not hesitate to contact me with any questions, and thank you in advance for your consideration.

\closing{Sincerely,}

% \encl{brownletter.cls}

% \ps{Please see the enclosed file.}

% \cc{J. Kirschenbaum}

\end{letter}

\end{document}