%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\usepackage{amsfonts,amsmath,amssymb,amsbsy,amstext,amsthm,mathtools}
\usepackage{hyperref}

\newcommand{\C}{\mathbb{C}}
\newcommand{\PP}{\mathbb{P}}


\name{Nesime Tatbul} % used as signature, if no signature is specified

\signature{Juliette Bruce}

\date{October 11, 2022} % if no date specified, today's date is used 

\subject{Cover Letter for Women in Commutative Algebra and Algebraic Geometry} % optional subject line

\begin{document}

\begin{letter}{Juliette Bruce,\\ 
               Brown University\\ 
               Providence, RI 02912}

\opening{To Whom It May Concern,}

My name is Juliette Bruce, and I am a postdoctoral research associate at Brown University, working in commutative algebra and algebraic geometry. I completed my Ph.D. in Mathematics at the University of Wisconsin - Madison in August 2020 under the guidance of Professor Daniel Erman. I am writing to apply to participate in the Women in Commutative Algebra and Algebraic Geometry conference.

This workshop seems like an amazing opportunity to build a network of connections (collaborators, mentors, friends) in commutative algebra and algebraic geometry. I think attending and building these connections would be extremely beneficial to my career as I make the transition from a post-doc to (hopefully) a tenure-track position. Further, my research interest are decidedly in commutative algebra and algebraic geometry, and so I feel that I will be able to positively contributed both mathematically and socially to this workshop. In particular, I am also excited by the opportunity to learn from the other participants and would fully commit to being an active and enthusiastic participants to all of the aspects of the workshop. In fact, I have really been looking forward to the next Women in Commutative Algebra event since 2019 when I was unable to participate in the first such workshop. 


My application includes a curriculum vitae, a brief research statement, this cover letter, and two letters of recommendation. One letter from Christine Berkesch (\href{mailto:cberkesc@umn.edu}{cberkesc@umn.edu}) with whom I have never collaborated, worked with at the same institution, or had as a supervisor. One letter from Melody Chan (\href{mailto:melody\_chan@brown.edu}{melody\_chan@brown.edu}) who is my postdoctoral supervisor at Brown University. 


Please do not hesitate to contact me with any questions, or if there is anything else I can provide, and thank you in advance for your consideration. 


\closing{Sincerely,}

% \encl{brownletter.cls}

% \ps{Please see the enclosed file.}

% \cc{J. Kirschenbaum}

\end{letter}

\end{document}