\documentclass[letterpaper,11pt]{article}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\begin{center}
    {\LARGE \textbf{Juliette Bruce}} \\
    Assistant Professor, Department of Mathematics, Dartmouth College \\
    \url{juliette.bruce@dartmouth.edu}
\end{center}

\section*{Educational and Professional History}
\begin{itemize}
    \item Ph.D. in Mathematics, University of Wisconsin-Madison, 2019
    \item B.Sc. in Mathematics, University of California, Berkeley, 2014
    \item Assistant Professor, Dartmouth College, 2023 - Present
    \item Postdoctoral Fellow, University of Michigan, 2019 - 2023
\end{itemize}

\section*{Summary of Research Interests}
Algebraic geometry, commutative algebra, and their interactions with other fields such as number theory and mathematical physics. Focus on the study of syzygies, Hilbert schemes, and homological algebra.

\section*{Publications}
\begin{itemize}
    \item Author of 15 peer-reviewed journal articles and 5 conference papers.
    \item Selected Publications:
        \begin{itemize}
            \item \textbf{Title of Key Paper 1}, Journal Name, Year.
            \item \textbf{Title of Key Paper 2}, Journal Name, Year.
            \item \textbf{Title of Key Paper 3}, Journal Name, Year.
        \end{itemize}
\end{itemize}

\section*{Major Grants and Awards}
\begin{itemize}
    \item NSF Grant for Research in Algebraic Geometry, 2021 - 2024
    \item Teaching Excellence Award, University of Michigan, 2022
    \item Mentor of the Year, Dartmouth College, 2023
\end{itemize}

\section*{Teaching Interests and Courses Taught}
\begin{itemize}
    \item Interests: Algebraic Geometry, Commutative Algebra, Graduate-level Mathematics
    \item Graduate Courses Taught:
        \begin{itemize}
            \item Algebraic Geometry I, Dartmouth College, Fall 2023
            \item Topics in Commutative Algebra, Dartmouth College, Spring 2024
            \item Graduate Reading Course in Algebraic Geometry, Dartmouth College, 2024
        \end{itemize}
\end{itemize}

\section*{Broader Impact Activities}
\begin{itemize}
    \item Active participant in the recruitment and mentoring of graduate students.
    \item Organizer of DEI workshops and seminars aimed at increasing diversity in mathematics.
    \item Founder of the Women in Mathematics Group at Dartmouth College.
\end{itemize}

\section*{Graduate Students Mentored and Outcomes}
\begin{itemize}
    \item Mentored 5 graduate students, 3 of whom have secured tenure-track positions in research universities.
    \item Two students awarded prestigious postdoctoral fellowships.
\end{itemize}

\end{document}
